Discrete Quantum Theories and Computing

### 2018-03-13 dissertation.tex
dissertation.lyx "3.3 Modal Quantum Computing" Updating...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{comment}
\usepackage[all]{xy}
\usepackage{framed}
\usepackage[braket,qm]{qcircuit}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{dsfont}

@@

Our computations with this ``toy'' modal quantum theory showed that
it possesses ``supernatural'' computational power. For example,
one can solve a black box version of the \usat\ problem~\cite{usat}
in a way that outperforms conventional quantum computing. The classical
\usat\ problem (also known as \texttt{USAT} or \texttt{UNAMBIGUOUS-SAT})
is the problem of deciding whether a given boolean formula has a satisfying
assignment, assuming that it has at most one such assignment~\cite{complexity}.
This problem is, in a precise sense~\cite{Valiant198685}, just as
hard as the general satisfiability problem and hence all problems
in the~NP complexity class. Our black-box version of the \usat\ problem
replaces the boolean formula with an arbitrary black box. Solutions
to this generalized problem can be used to solve an unstructured database
search of size $N$ using $O(\log{N})$ black box evaluations by binary
search on the database. This algorithm then outperforms the known
asymptotic bound $O(\sqrt{N})$ for unstructured database search in
conventional quantum computing.

\begin{figure}[t]
\[
\begin{array}{@{\!\!}c}
\hspace*{1.35cm}\xymatrix@C=0pt{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes S} & \ghost{\uf} & \multigate{2}{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
\lstick{\ldots} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
\lstick{x_{n}=\ket{0}} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}
}
\end{array}
\]
\caption[]{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
over the field $\ff{2}$. $\uf$ is a Deutsch quantum black box~\cite{NCbook}
with $\uf\ket{y}\ket{\overline{x}}~=~\ket{y\scalarPlus f(\overline{x})}\ket{\overline{x}}$,
where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
of $n$ bits. For further notation see text.}
\end{figure}

@@

\bibitem{VY} Veblen O and J. W. Young J W 1946 \textit{Projective
Geometry Vol. 2} (Blaisdell Publishing Company), pp 55–57

@@

\begin{figure}[t]
\[
\begin{array}{c}
\hspace*{1.5cm}\xymatrix@C=0pt{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
\lstick{x_{1}=\ket{0}} & \multigate{2}{H} & \ghost{\uf} & \multigate{2}{H} & \ghost{\text{measure}}\\
\lstick{\ldots} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}\\
\lstick{x_{n}=\ket{0}} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}
}
\end{array}
\]
\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
\label{fig:dbsearch} 
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{comment}
\usepackage{framed}
\usepackage[braket,qm]{qcircuit}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{dsfont}

\usepackage[all]{xy}
\newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
\newcommand{\xyC}[1]{\xymatrixcolsep={#1}}

@@

Our computations with this ``toy'' modal quantum theory showed that
it possesses ``supernatural'' computational power. For example,
one can solve a black box version of the \usat\ problem~\cite{usat}
in a way that outperforms conventional quantum computing. The classical
\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$\todo{Add
citation about where these two names come from.}) is the problem
of deciding whether a given boolean formula has a satisfying assignment,
assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
This problem is, in a precise sense~\cite{Valiant198685}, just as
hard as the general satisfiability problem and hence all problems
in the~NP complexity class. Our black-box version of the \usat\ problem
replaces the boolean formula with an arbitrary black box. Solutions
to this generalized problem can be used to solve an unstructured database
search of size $N$ using $O\left(\log N\right)$ black box evaluations
by binary search on the database. This algorithm then outperforms
the known asymptotic bound $O\left(\sqrt{N}\right)$ for unstructured
database search in conventional quantum computing.

\begin{figure}[t]
\[
\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \gate{~S^{\dagger}~} & \ctrl{3} & \gate{~S^{\dagger}~} & \multimeasureD{3}{\text{measure}}\\
\lstick{x_{1}=\ket{0}} & \multigate{2}{\otimes S} & \ghost{\uf} & \multigate{2}{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
\lstick{\ldots} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}\\
\lstick{x_{n}=\ket{0}} & \ghost{\otimes S} & \ghost{\uf} & \ghost{\otimes S} & \targ & \qw & \ghost{\text{measure}}
}
\]
\caption{\label{fig:alg}Circuit for black box \usat\ in modal quantum theory
over the field $\ff{2}$. $\uf$ is a Deutsch quantum black box~\cite{544199}
with $\uf\ket{y}\ket{\overline{x}}~=~\ket{y\scalarPlus f(\overline{x})}\ket{\overline{x}}$,
where $\overline{x}$ denotes a sequence $x_{1},x_{2},\ldots,x_{n}$
of $n$ bits. For further notation see text.}
\end{figure}

@@

\bibitem{VY} Veblen O and J. W. Young J W 1946 \textit{Projective
Geometry Vol. 2} (Blaisdell Publishing Company), pp 55??7

@@

\begin{figure}[t]
\[
\xyR{.9em}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix{\lstick{y=\ket{0}} & \qw & \multigate{3}{\uf} & \qw & \multimeasureD{3}{\text{measure}}\\
\lstick{x_{1}=\ket{0}} & \multigate{2}{H} & \ghost{\uf} & \multigate{2}{H} & \ghost{\text{measure}}\\
\lstick{\ldots} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}\\
\lstick{x_{n}=\ket{0}} & \ghost{H} & \ghost{\uf} & \ghost{H} & \ghost{\text{measure}}
}
\]
\caption[]{Circuit for black box \usat\ in discrete quantum computing.}
\label{fig:dbsearch} 
\end{figure}
